Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-05 paper.tex
Add multimedia extensions in appendix.

\usepackage{array} 
\usepackage{mdwmath}
\usepackage{mdwtab}

@@

>>>>

\usepackage{float}
\restylefloat{table}
\usepackage{array} 
\usepackage{mdwmath}
\usepackage{mdwtab}

@@

\appendix
\section{Index to Multimedia Extensions}

\begin{table}[H]
\begin{tabular}{c c m{0.7\linewidth}}
Extension & Type & Description \\
\hline
1 & Video & Example of a constrained motion planning result executed
on HRP-2. \\
2 & Video & Chairs scenario: solution of whole-body planning executed
on HRP-2. \\
3 & Video & Shelf scenario: solution of whole-body planning executed
in simulation and on HRP-2. \\
4 & Data & Raw data of sliding motion planning benchmarks for all
scenarios. \\
\end{tabular}
\end{table}
